Foundational claims of group polarization are plausibly false, with lessons for the empirical study of psychological dynamics

### 2024-11-04 GroupPolarizationStatmod/paper/ms.tex
outlined results subsections

\newcommand{\thetafit}{\theta_\mathrm{fit}}

@@

\subsection{Eighty percent false detection rate across corpus for $d^*=0.8$?}

\subsection{What $d^*$ is necessary to achieve magical $\alpha = 0.05$?}

>>>>

\newcommand{\thetafit}{\theta^\mathrm{fit}}

@@

\subsection{False detection rates exceed ??\% even at ``high significance''}

\mt{Graph with $\alpha(d^*)$ for $d^* = 0.2,~0.5,~0.8$ for each condition,
each article aggregated, and across all conditions/articles. Use color-coding for
each article, stems with dots at end, red to yellow gg2 theme, in order of
appearance.}

\subsection{Minimum $d^*$ for FWER of 0.05}

Solving the inverse problem of which $d^*$ achieves a low family-wise error rate,
which drives the false detection rate. Here we present our calculations to find
$d^*$ that achieve $\alpha(d^*) = 0.05$, a commonly-assumed parameter value of
metascience.
